\documentclass{article}
\usepackage{graphics}

\setlength{\parindent}{0pt}
\newfont{\fontcream}{cream}
%\newfont{\fontcream}{ParcPlace}
\renewcommand{\part}[1]{
  \begin{center}
    \textbf{#1}
  \end{center}
  \fontcream
}

\begin{document}

\noindent

\part{obligatory typesetting copypasta}

the quick brown fox jumps over the lazy dog

\part{I. Eruption}

\part{II. Stones of Years}

has the dawn ever seen your eyes?
have the days made you so unwise?
realize you are,
had you talked to the winds of time?
then you'd know how the waters rhyme
- taste of wine

how can you know where you've been
in time you'll see the sign,
and realize your sin,
will you know how the seed is sown
all your time has been overgrown
- never known

have you walked on the stones of years?
when you speak is it you that hears?
are your ears full?
you can't hear anything at all

\part{III. Iconoclast}

\part{IV. Mass}

the preacher said a prayer,
save every single hair on his head
- he's dead

the minister of hate had just arrived, too late to be spared
- who cared
the weaver in the web that he made

the pilgrim wandered in,
commiting every sin that he could
- so good

the cardinal of grief was set in his belief he'd saved
- from the grave
the weaver in the web that he made

the high priest took a blade,
to bless the ones that prayed
and all obeyed

the messenger of fear is slowly growing nearer to the time
- a sign
the weaver in the web that he made

a bishops rings a bell,
a cloak of darkness fell across the ground
- without a sound

the silent choir sing and in their silence
bring jaded sound harmonic ground
- the weaver in the web that he made

\part{V. Manticore}

\part{VI. The Battlefield}

clear the battlefield and let me see,
all the profit from our victory,
you talk of freedom starving children fall,
are you deaf when you hear the seasons call

were you there to watch the earth be scorched?
did you stand beside the spectral torch,
know the leaves of sorrow turned their face,
scattered on the ashes of disgrace,

every blade is sharp the arrows fly,
where the victims of your armies lie,
where the blades of grass and arrows rain,
then there will be no sorrow,
be no pain

\end{document}
